Incentivizing Exploration with Unbiased Histories

### 2019-04-29 ec19 workshops/cover-straregic-learning.tex
Minor edit.

This paper continues the line of work on ``incentivized exploration": essentially, bandit learning in applications such as recommendation systems, in the presence of strategic behavior of self-interested users whose incentives are skewed in favor of exploitation. As such, this paper continues a broader theme of ``exploration and incentives", and is firmly positioned in the area of ``learning in the presence of strategic behavior". This is the first paper in the literature on ``exploration and incentives" (and possibly in the broader literature on ``learning and incentives") which attempts to mitigate the limitations of standard economic assumptions on rational behavior.
\end{document}

>>>>

This paper continues the line of work on ``incentivized exploration": essentially, bandit learning in applications such as recommendation systems, in the presence of strategic behavior of self-interested users whose incentives are skewed in favor of exploitation. As such, this paper continues a broader theme of ``exploration and incentives", and is firmly positioned in the area of ``learning in the presence of strategic behavior". To the best of our knowledge, this is the first paper in the literature on ``exploration and incentives" (and possibly in the broader literature on ``learning and incentives") which attempts to mitigate the limitations of standard economic assumptions on rational behavior.
\end{document}
